Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-11 WSSSPE4_report/WSSSPE4_report.tex
fixing more small wording; again will update arXiv later

To investigate best practices for scientific software we brought together a panel of five experts with different perspectives on ``Best Practices for Scientific Software.''
These were: Alice Allen, Editor, Astrophysics Source Code Library, brought an understanding of the difficulties of organizing a community and curating their software;
Mike Croucher from the University of Sheffield and Rob Haines from the University of Manchester who are both Research Software Engineers with decades of experience of writing code for researchers;
Patricia Lago from Vrije Universiteit Amsterdam presented a keynote at the workshop (\S\ref{sec:keynote}) and brought a fresh perspective on software sustainability from the point of view of its impact on society and business; and
Karthik Ram from the Berkeley Institute for Data Science brought his perspective on the practicalities of using scientific software to conduct his research as a data scientist.

>>>>

To investigate best practices for scientific software we brought together a panel of five experts with different perspectives on ``Best Practices for Scientific Software.''
These were: Alice Allen, Editor, Astrophysics Source Code Library, who brought an understanding of the difficulties of organizing a community and curating their software;
Mike Croucher from the University of Sheffield and Rob Haines from the University of Manchester who are both Research Software Engineers with decades of experience of writing code for researchers;
Patricia Lago from Vrije Universiteit Amsterdam, who presented a keynote at the workshop (\S\ref{sec:keynote})  and brought a fresh perspective on software sustainability from the point of view of its impact on society and business; and
Karthik Ram from the Berkeley Institute for Data Science, who brought his perspective on the practicalities of using scientific software to conduct his research as a data scientist.
